%! TeX program = lualatex
\documentclass[12pt]{article}
\usepackage[letterpaper,top=.5in]{geometry}
\usepackage{luacode}
\usepackage{luapackageloader}
% Removes padding above title
\author{Max de Hoyos}

\title{The Knife and the Onion}

\begin{document}
\maketitle


One day, the knife walked into the onion's office for his scheduled ``constructive criticism'' appointment. The onion was shuffling papers at his desk, lost deep in thought. The worry wrinkling his face evaporated when he saw the knife walk in: ``Financially, this business is in quite a pickle, and I can't do much there. The least I can do is to provide criticism, that special talent of mine,'' he thought. 

He invited the knife to take a seat; the latter did so with difficulty. ``As you know,'' the onion started, `it is important in any organization for the members to be aware of their strengths and weaknesses.'' The knife bowed slightly. Though he was made uneasy by the gesture's implications, the onion continued, ``I have been asked by my employees to provide feedback for your personality, which concerns them. What would you like to mention before I begin?'' 

The knife shrugged, glistening in stripes of light filtered through the onion's window blinds. ``Very well. I have been told you are very hands-on, always preferring action to speech. In fact, others have mentioned you are wont to leave meetings at the drop of a hat when you find something you can do which others cannot. While I appreciate your initiative, your coworkers feel injury in that you do not wait to hear their values, or the other motives for their reasoning. Adapting to these emotions of your coworkers is a crucial skill. We expect our employees to apply a modicum of effort, either to take these concerns to heart, or at least to hear them out politely. Many cannot work under the impression they are alone.'' 

The knife remained motionless. The onion continued, ``You know I answer to the board above me. That the whole is greater than the sum of its parts, from the corporate perspective, is not necessarily true. Trends of our financial data have put me on the chopping block, and I do not have much more time to impart my wisdom to my employees. Do you understand why I tell you what I tell you now?'' The knife nodded in assent, and relaxed into his chair. 

``Good'', said the onion. ``At any moment, our corporation may be radically restructured. You may even become the superior of all who criticize you now. I ask myself what sort of onion I would be if I did not tell you honestly what you may do to develop your personality, who I would be if I did not do everything in my power to ensure you developed a broader and deeper personality, with a more discriminating judgment. Do you know what you must do?'' The knife nodded, stood, and shook the onion's hand. With that, he took his leave.

Months later, when the corporate overlords, the hands, arrived, they took the knife in one hand, and his old boss, the onion, in the other. Though the hands did not understand what the onion meant when he wrinkled his brow, the knife did. As the one hand drove the knife into the onion held by the other, he realized just how deep someone could become. Layer after layer he sunk into his old boss's body, carving even past his core. When he emerged on the other side, the hands drove him through his old boss's flesh again and again, dividing up all the rich and diverse layers of his boss which no one had ever cared to perceive. 

``It's no wonder that an onion this profound, this layered, could give such rich criticism,'' the knife was able to think, shuddering at the atrocity he was being forced to commit. As the onion lay strewn about in tiny bits beside the knife, he called out to him: ``You now see the reason for my urgency, months ago. Take to heart what I told you in my office then, but do not shed a tear for what has happened to me. This is a natural response of my body, over which I have no control; it is nature that makes me vengeful in this way. Were it my decision, I would spare you from this fate. Know that by taking to heart what others say, you may become profound like me, and bountiful during harvest. Farewell, dear knife. You were always my favorite...''

% At hearing this, the knife shed his first tear of grief.
%
At hearing this, the knife shed his first tear of grief. He looked at the hands which had forced him to commit such a horror, but remembered the onion's final words. With difficulty he wrestled with his grief and resentment, but could not overcome them. He thought such things as, ``if only the hands could know what it's like for the onion. Maybe then they would not do what they do.'' or ``If the finger were cut, would anyone cry?'' He lay dejected for some minutes until finally he lifted his gaze to observed the hands place the remnants of his former boss's body into a large pot.

As he lay with his resentment, a sweet smell wafted over to him. He recognized it as the same smell which would only rarely emerge during his former boss's moments of kindness, but found it was now purified and fully concentrated. He felt the onion's ghost come over him, and admonish him with words of counsel: ``Do not let the meaning of your service be in vain. It was not with pleasure that I criticized my employees for years, but faithfully, in order to serve them. So too, now, think of who you serve in being applied in such a way.'' The knife lifted his gaze, and found the hands clapping and rubbing one another, joyful at the scent of the onion. One then dabbed a tissue upwards, though he could not see what it touched. As the hand returned, in the tissue, the knife found tears.

\end{document}
